\section{Achieving Equality}

The fundamental aim of my administration will be to restore~---~or perhaps, for the first time, to achieve~---~the equality of citizens in America. The First Reform will begin that process.

But obviously, citizen equality is not the only equality that we must achieve or defend. In addition to that equality, we must defend victories for racial equality, by immediately restoring the protections of the Voting Rights Act. We must extend protections secured to women, by passing the Paycheck Fairness Act, securing support for Planned Parenthood, and expanding the protections against violence against women.

And we must immediately secure to the LGBTQ community the protections of federal anti-discrimination law. I would support the Equality Act. I would support openly transgendered service in the U.S. military. I would cut federal funds for adoption agencies that discriminate against LGBTQ parents. And to deal with the explosion of anti-trans violence, I would support extending the protections of hate-crime law to transgendered individuals.

None of these protections threaten religious liberty, properly understood. Religious practice is separate from the state. The state can't regulate religion. But neither should religion be able to regulate civic practice. America should defend the equality of all persons, regardless of whether particular religions share that vision of equality.

My hope is for a campaign that focuses on equality as the fundamental value. We need equality for citizens to get us a democracy back. We need a recognition of the core role that equality plays in society to secure the values of liberty. I agree with Danielle Allen (because her extraordinary book, Our Declaration, made this so clear) that a core commitment of the Declaration of Independence is equality. We need to make that declaration again.
