\chapter{The First Reform}

The first priority of a Lessig administration would be to fix the corruption that has crippled Congress, by enacting legislation to restore the fundamental principle of a representative democracy: the equality of citizens.

That legislation~---~the Citizen Equality Act~---~is described in detail in the next section. 
Its basic objective is to give to each citizen an equal stake in our democracy, so that our government responds to all of us, and not just to the few.

Passing this legislation would make practically every other policy described on this issues page easier to achieve. In some cases, passing this legislation is the only way these other policies could be achieved. And throughout the descriptions of these other policies, I will highlight the ways in which this corrupted inequality makes achieving the right answer difficult, if not impossible.

\section{Citizen Equality Act of 2017}

The Citizen Equality Act is our vision of the reforms we need to fix our democracy.

Together, these reforms will fundamentally change the way our government works. They will fulfill the promise of American democracy: a government of, by, and for the people.

Each part is modeled off of existing proposals. As our campaign grows, we will crowdsource a process to complete the details of this reform and draft legislation by the start of 2016.

\subsection{Equal Right to Vote}

All citizens deserve equal access to the ballot.

The Citizen Equality Act will guarantee the equal freedom to vote by passing the Voting Rights Advancement Act of 2015 and the Voter Empowerment Act of 2015. In addition, we will enact automatic voter registration and turn election day into a national holiday.

\subsection{Equal Representation}

All citizens deserve equal representation in Congress.

The Citizen Equality Act will give each voter as close to equal political influence as possible by redrawing districts and restructuring election systems. It will use FairVote's ``Ranked Choice Voting Act'' to end political gerrymandering and create multi-member districts with ranked-choice voting for Congress.

\subsection{Citizen Funded Elections}

All citizens deserve an equal ability to choose our leaders.

The Citizen Equality Act will end pay-to-play politics by changing the way we fund campaigns by taking the best of  Rep. Sarbanes' Government by the People Act, and Represent.US's ``American Anti-Corruption Act.'' That hybrid would give every  voter a voucher to contribute to fund congressional and presidential campaigns; it would provide matching funds for small-dollar contributions to congressional and presidential campaigns. And it would add effective new limits to restrict the revolving door between government service and work as a lobbyist.
