\section{The Internet}

The Internet is infrastructure for the 21st century. It is the most important driver of economic and social transformation in America in our lifetime. It is an engine of growth and innovation, and the core technology protecting the freedom of speech.

But the Internet is threatened by economic and political interests that don't like the freedom and innovation that it enables. They in turn use their power, both economic and through government, to change the Internet and restrict its freedoms.

The fight to defend ``network neutrality'' against this threat represents one of the most important victories that Internet activists can celebrate. Millions rallied to demand the FCC protect the freedom to innovate, by requiring that the network remain neutral. Yet almost immediately after that victory, lobbyists on Capitol Hill began a campaign to undo this Internet freedom.

As President, no issue would be more natural to me. I have spent much of my career defending the freedoms of the network and fighting to expand its reach. I helped found Creative Commons. I served on the board of EFF and the Free Software Foundation, and was awarded the Free Software Foundation's Freedom Award. No one running for President could have a stronger commitment to defend the values of the Internet than I.

But the Internet will not be safe from the meddling of cronies or corrupted capitalists until we free Congress from their influence. Until the The First Reform is enacted, network neutrality will be threatened. After it is enacted, the view that this network is essential infrastructure, which must be equally and broadly deployed, will be easier to sustain.
