\section{The So-Called ``War on Drugs''}

The ``war on drugs'' has been the most self-destructive war in American history since the Civil War. Motivated by the same naive idea that led America into prohibition, the war has cost billions of dollars, and countless American lives; it has weakened the law's protection for civil rights, and it has destroyed the security and democracy of the many South and Central American nations drawn into the illegal drug trade.

We must acknowledge the mistake of this war. Not the mistake in its objective~---~to protect the vulnerable against debilitating addiction. Instead, the mistake in its means. Addiction is a disease whose nature and cause we don't yet fully understand. But we should treat it like a disease, with compassion and support, and with the hope that gives people the strength to turn away from their drug.

I therefore support the legalization of marijuana~---~not because I want my children to use that drug, but because I recognize the limits of government's power in a free society. I would also press the federal government to develop plans to decriminalize other controlled substances~---~at least when it is clear that the cost of prohibition exceeds any benefit to society.

But we should recognize the forces that block sensible drug policy in America today. Prison guard unions have opposed decriminalization. Private prisons have spent millions to oppose policies that reduce the number of ``criminals'' in the system. Pharmaceutical companies have opposed changes that would create new competition to their own drugs. Alcohol and beer organizations have given millions to oppose candidates who support legalization. These forces are the corruption that The First Reform would attack. This policy change will be possible once that first reform is enacted.
